### 2023-03-21 src/paper.tex
Add more examples

\newcommand{\NT}[1]{{#1}}
\newcommand{\T}[1]{{#1}}
\newcommand{\Var}[1]{{#1}}
\newcommand{\Sym}[1]{{#1}}

@@

\subsubsection{Vsebovanje}
Nekaj znotraj nečesa.
\begin{equation*}
  \begin{aligned}[t]
    \NT{B} &\Arrow \T{l} \Spc \T{I} \Spc \T{r}\\
    \NT{I} &\Arrow \T{i}\\[1em]
    \NT{Box} &\Arrow \T{lbrac} \Spc \NT{Val} \Spc \T{rbrac}\\
    \NT{Val} &\Arrow \T{num} \Union \T{star}\\[1em]
    \T{num} &= \KleenePlus{\{\Char{0}, \dots, \Char{9}\}}\\
    \T{lbrac} &= \Char{[}\\
    \T{rbrac} &= \Char{]}\\
    \T{star} &= \Char{*}
  \end{aligned}
\end{equation*}
\begin{lstlisting}
[*]
[1]
\end{lstlisting}

\begin{equation*}
  \begin{aligned}[t]
    \NT{B} &\Arrow \T{l} \Spc \T{L} \Spc \T{r}\\
    \NT{L} &\Arrow \T{i} \Spc \NT{L'}\\
    \NT{L'} &\Arrow \T{s} \Spc \T{i} \Spc \NT{L'} \Union \Null\\[1em]
    \NT{Box} &\Arrow \T{lbrac} \Spc \NT{Numbers} \Spc \T{rbrac}\\
    \NT{Numbers} &\Arrow \T{num} \Spc \NT{Numbers'}\\
    \NT{Numbers'} &\Arrow \T{sep} \Spc \T{num} \Spc \NT{Numbers'} \Union \Null\\[1em]
    \T{num} &= \KleenePlus{\{\Char{0}, \dots, \Char{9}\}}\\
    \T{lbrac} &= \Char{[}\\
    \T{rbrac} &= \Char{]}\\
    \T{sep} &= \Char{+}
  \end{aligned}
\end{equation*}
\begin{lstlisting}
[1]
[1 + 2]
[1 + 2 + 3]
\end{lstlisting}

@@

\begin{equation*}
  \begin{aligned}[t]
    \NT{B} &\Arrow \T{l} \Spc \NT{B} \Spc \T{r} \Union \NT{I}\\[1em]
    \NT{I} &\Arrow \T{i}\\
    \NT{Box} &\Arrow \T{lbrac} \Spc \NT{Box} \Spc \T{rbrac} \Union \NT{Val}\\
    \NT{Val} &\Arrow \T{num} \Union \T{star}\\[1em]
    \T{num} &= \KleenePlus{\{\Char{0}, \dots, \Char{9}\}}\\
    \T{lbrac} &= \Char{[}\\
    \T{rbrac} &= \Char{]}\\
    \T{star} &= \Char{*}
  \end{aligned}
\end{equation*}
\begin{lstlisting}
[*]
[[[1]]]
[[[[[[[1]]]]]]]
\end{lstlisting}

\begin{equation*}
  \begin{aligned}[t]
    \NT{L} &\Arrow \NT{I} \Spc \NT{L'}\\
    \NT{L'} &\Arrow \T{s} \Spc \NT{I} \Spc \NT{L'} \Union \Null\\
    \NT{I} &\Arrow \T{i} \Union \NT{L}\\[1em]
    \NT{Numbers} &\Arrow \T{Val} \Spc \NT{Numbers'}\\
    \NT{Numbers'} &\Arrow \T{sep} \Spc \T{Val} \Spc \NT{Numbers'} \Union \Null\\
    \NT{Val} &\Arrow \T{num} \Union \T{lbrac} \Spc \NT{Numbers} \Spc \T{rbrac}\\[1em]
    \T{num} &= \KleenePlus{\{\Char{0}, \dots, \Char{9}\}}\\
    \T{lbrac} &= \Char{[}\\
    \T{rbrac} &= \Char{]}\\
    \T{sep} &= \Char{+}
  \end{aligned}
\end{equation*}
\begin{lstlisting}
[1]
[[[1] + [2] + [3]]]
[[1 + [2] + [1 + 2 + 3]]]
\end{lstlisting}

@@

>>>>

\newcommand{\NT}[1]{{#1}}
\newcommand{\T}[1]{{#1}}
\newcommand{\Var}[1]{{#1}}
\newcommand{\Sym}[1]{{#1}}
\newcommand{\Lookahead}[1]{{}_{\{{#1}\}}}

@@

\subsubsection{Vsebovanje}
Nekaj znotraj nečesa.
\begin{equation*}
  \begin{aligned}[t]
    \NT{B} &\Arrow \T{l} \Spc \T{I} \Spc \T{r}\\
    \NT{I} &\Arrow \T{i}\\[1em]
    \NT{Box} &\Arrow \T{lbrak} \Spc \NT{Val} \Spc \T{rbrak}\\
    \NT{Val} &\Arrow \T{num} \Union \T{star}\\[1em]
    \T{num} &= \KleenePlus{\{\Char{0}, \dots, \Char{9}\}}\\
    \T{lbrak} &= \Char{[}\\
    \T{rbrak} &= \Char{]}\\
    \T{star} &= \Char{*}
  \end{aligned}
\end{equation*}
\begin{lstlisting}
[*]
[1]
\end{lstlisting}

\begin{equation*}
  \begin{aligned}[t]
    \NT{B} &\Arrow \T{l} \Spc \T{L} \Spc \T{r}\\
    \NT{L} &\Arrow \T{i} \Spc \NT{L'}\\
    \NT{L'} &\Arrow \T{s} \Spc \T{i} \Spc \NT{L'} \Union \Null\\[1em]
    \NT{Box} &\Arrow \T{lbrak} \Spc \NT{Numbers} \Spc \T{rbrak}\\
    \NT{Numbers} &\Arrow \T{num} \Spc \NT{Numbers'}\\
    \NT{Numbers'} &\Arrow \T{sep} \Spc \T{num} \Spc \NT{Numbers'} \Union \Null\\[1em]
    \T{num} &= \KleenePlus{\{\Char{0}, \dots, \Char{9}\}}\\
    \T{lbrak} &= \Char{[}\\
    \T{rbrak} &= \Char{]}\\
    \T{sep} &= \Char{+}
  \end{aligned}
\end{equation*}
\begin{lstlisting}
[1]
[1 + 2]
[1 + 2 + 3]
\end{lstlisting}

@@

\begin{equation*}
  \begin{aligned}[t]
    \NT{B} &\Arrow \T{l} \Spc \NT{B} \Spc \T{r} \Union \NT{I}\\[1em]
    \NT{I} &\Arrow \T{i}\\
    \NT{Box} &\Arrow \T{lbrak} \Spc \NT{Box} \Spc \T{rbrak} \Union \NT{Val}\\
    \NT{Val} &\Arrow \T{num} \Union \T{star}\\[1em]
    \T{num} &= \KleenePlus{\{\Char{0}, \dots, \Char{9}\}}\\
    \T{lbrak} &= \Char{[}\\
    \T{rbrak} &= \Char{]}\\
    \T{star} &= \Char{*}
  \end{aligned}
\end{equation*}
\begin{lstlisting}
[*]
[[[1]]]
[[[[[[[1]]]]]]]
\end{lstlisting}

\begin{equation*}
  \begin{aligned}[t]
    \NT{L} &\Arrow \NT{I} \Spc \NT{L'}\\
    \NT{L'} &\Arrow \T{s} \Spc \NT{I} \Spc \NT{L'} \Union \Null\\
    \NT{I} &\Arrow \T{i} \Union \NT{L}\\[1em]
    \NT{Numbers} &\Arrow \T{Val} \Spc \NT{Numbers'}\\
    \NT{Numbers'} &\Arrow \T{sep} \Spc \T{Val} \Spc \NT{Numbers'} \Union \Null\\
    \NT{Val} &\Arrow \T{num} \Union \T{lbrak} \Spc \NT{Numbers} \Spc \T{rbrak}\\[1em]
    \T{num} &= \KleenePlus{\{\Char{0}, \dots, \Char{9}\}}\\
    \T{lbrak} &= \Char{[}\\
    \T{rbrak} &= \Char{]}\\
    \T{sep} &= \Char{+}
  \end{aligned}
\end{equation*}
\begin{lstlisting}
[1]
[[[1] + [2] + [3]]]
[[1 + [2] + [1 + 2 + 3]]]
\end{lstlisting}

@@

\section*{Primeri}

\subsection{Seznam}

\subsubsection*{Jezik}
\begin{verbatim}
  [1]
\end{verbatim}
\begin{verbatim}
  [1, 2, "abc", 3]
\end{verbatim}

\subsubsection*{Regularni izrazi}
\begin{equation*}
  \begin{aligned}
    \T{int} &= \KleenePlus{\{\Char{0}, \dots, \Char{9}\}}\\
    \T{string} &= \Char{"} \Spc \Kleene{(\Alphabet - \{\Char{"}\})} \Spc \Char{"}\\
    \T{comma} &= \Char{,}\\
    \T{lbrak} &= \Char{[}\\
    \T{rbrak} &= \Char{]}\\
  \end{aligned}
\end{equation*}

\subsubsection*{Gramatika}
\begin{equation*}
  \begin{aligned}
    \NT{Start} &\Arrow \NT{List}\\
    \NT{List} &\Arrow \T{lbrak} \Spc \NT{Items} \Spc \T{rbrak}\\
    \NT{Items} &\Arrow \NT{Item} \Spc \NT{Items'}\\
    \NT{Items'} &\Arrow \T{comma} \Spc \NT{Items} \Union \Null\\
    \NT{Item} &\Arrow \T{int} \Union \T{string}
  \end{aligned}
\end{equation*}

\subsubsection*{{\FIRST} \& {\FOLLOW}}
\begin{equation*}
  \begin{aligned}
    \FIRST(\T{int}) &= \{\T{int}\}\\
    \FIRST(\T{string}) &= \{\T{string}\}\\
    \FIRST(\T{comma}) &= \{\T{comma}\}\\
    \FIRST(\T{lbrak}) &= \{\T{lbrak}\}\\
    \FIRST(\T{rbrak}) &= \{\T{rbrak}\}\\
    \FIRST(\NT{Item}) &= \{\T{int}, \T{string}\}\\
    \FIRST(\NT{Item'}) &= \{\T{comma}\}\\
    \FIRST(\NT{Items}) &= \{\T{int}, \T{string}\}\\
    \FIRST(\NT{List}) &= \{\T{lbrak}\}\\
    \FIRST(\NT{Start}) &= \{\T{lbrak}\}\\
    \FIRST(\T{comma} \Seq \NT{Items}) &= \{\T{comma}\}\\
    \FIRST(\NT{Item} \Seq \NT{Items'}) &= \{\T{int}, \T{string}\}\\
    \FIRST(\T{lbrak} \Seq \NT{Items} \Seq \T{rbrak}) &= \{\T{lbrak}\}\\[1em]
    \FOLLOW(\NT{Start}) &= \{\EOF\}\\
    \FOLLOW(\NT{List}) &= \{\EOF\}\\
    \FOLLOW(\NT{Items}) &= \{\T{rbrak}\}\\
    \FOLLOW(\NT{Items'}) &= \{\T{rbrak}\}\\
    \FOLLOW(\NT{Item}) &= \{\T{comma}\}
  \end{aligned}
\end{equation*}

\begin{equation*}
  \begin{aligned}
    \FIRST(\FIRST(\T{List}) \Seq \FOLLOW(\NT{Start})) &= \{\T{lbrak}\}\\
    \FIRST(\FIRST(\T{lbrak} \Seq \NT{Items} \Seq \T{rbrak}) \Seq \FOLLOW(\NT{List})) &= \{\T{lbrak}\}\\
    \FIRST(\FIRST(\NT{Item} \Seq \NT{Items'}) \Seq \FOLLOW(\NT{Items})) &= \{\T{int, string}\}\\
    \FIRST(\FIRST(\T{comma} \Seq \NT{Items}) \Seq \FOLLOW(\NT{Items'})) &= \{\T{comma}\}\\
    \FIRST(\FIRST(\Null) \Seq \FOLLOW(\NT{Items'})) &= \{\T{rbrak}\}\\
    \FIRST(\FIRST(\T{int}) \Seq \FOLLOW(\NT{Item})) &= \{\T{int}\}\\
    \FIRST(\FIRST(\T{string}) \Seq \FOLLOW(\NT{Item})) &= \{\T{string}\}\\
  \end{aligned}
\end{equation*}

\begin{equation*}
  \begin{aligned}
    \NT{Start} &\Arrow \Lookahead{\T{lbrak}} \NT{List}\\
    \NT{List} &\Arrow \Lookahead{\T{lbrak}} \T{lbrak} \Spc \NT{Items} \Spc \T{rbrak}\\
    \NT{Items} &\Arrow \Lookahead{\T{int}, \T{string}} \NT{Item} \Spc \NT{Items'}\\
    \NT{Items'} &\Arrow \Lookahead{\T{comma}} \T{comma} \Spc \NT{Items} \Union \Lookahead{\T{rbrak}} \Null\\
    \NT{Item} &\Arrow \Lookahead{\T{int}} \T{int} \Union \Lookahead{\T{string}} \T{string}
  \end{aligned}
\end{equation*}

\subsection{Slovar}

\subsubsection*{Jezik}
\begin{verbatim}
  {}
\end{verbatim}
\begin{verbatim}
  {
    "a": 1;
    "b": "c";
    "d": {};
  }
\end{verbatim}

\subsubsection*{Regularni izrazi}
\begin{equation*}
  \begin{aligned}
    \T{int} &= \KleenePlus{\{\Char{0}, \dots, \Char{9}\}}\\
    \T{string} &= \Char{"} \Spc \Kleene{(\Alphabet - \{\Char{"}\})} \Spc \Char{"}\\
    \T{colon} &= \Char{:}\\
    \T{semi} &= \Char{;}\\
    \T{lbrac} &= \Char{\{}\\
    \T{rbrac} &= \Char{\}}\\
  \end{aligned}
\end{equation*}

\subsubsection*{Gramatika}
\begin{equation*}
  \begin{aligned}
    \NT{Start} &\Arrow \NT{Dict}\\
    \NT{Dict} &\Arrow \T{lbrac} \Spc \NT{Entries} \Spc \T{rbrac}\\
    \NT{Entries} &\Arrow \NT{Entry} \Spc \T{semi} \Spc \NT{Entries} \Union \Null\\
    \NT{Entry} &\Arrow \T{string} \Spc \T{colon} \Spc \NT{Value}\\
    \NT{Value} &\Arrow \T{int} \Union \T{string} \Union \NT{Dict}
  \end{aligned}
\end{equation*}

\subsubsection*{{\FIRST} \& {\FOLLOW}}
\begin{equation*}
  \begin{aligned}
    \FIRST(\T{int}) &= \{\T{int}\}\\
    \FIRST(\T{string}) &= \{\T{string}\}\\
    \FIRST(\T{semi}) &= \{\T{semi}\}\\
    \FIRST(\T{lbrac}) &= \{\T{lbrac}\}\\
    \FIRST(\T{rbrac}) &= \{\T{rbrac}\}\\
    \FIRST(\NT{Dict}) &= \{\T{lbrac}\}\\
    \FIRST(\NT{Value}) &= \{\T{int}, \T{string}, \T{lbrac}\}\\
    \FIRST(\NT{Entry}) &= \{\T{string}\}\\
    \FIRST(\NT{Entries}) &= \{\T{string}\}\\
    \FIRST(\NT{First}) &= \{\T{lbrac}\}\\
    \FIRST(\T{string} \Seq \T{colon} \Seq \NT{Value}) &= \{\T{string}\}\\
    \FIRST(\NT{Entry} \Seq \T{semi} \Seq \NT{Entries}) &= \{\T{string}\}\\
    \FIRST(\T{lbrac} \Seq \NT{Entries} \Seq \T{rbrac}) &= \{\T{lbrac}\}\\[1em]
    \FOLLOW(\NT{Start}) &= \{\EOF\}\\
    \FOLLOW(\NT{Dict}) &= \{\EOF\}\\
    \FOLLOW(\NT{Entries}) &= \{\T{rbrac}\}\\
    \FOLLOW(\NT{Entry}) &= \{\T{semi}\}\\
    \FOLLOW(\NT{Value}) &= \{\T{semi}\}
  \end{aligned}
\end{equation*}

\begin{equation*}
  \begin{aligned}
    \FIRST(\FIRST(\NT{Dict}) \Seq \FOLLOW(\NT{Start})) &= \{\T{lbrac}\}\\
    \FIRST(\FIRST(\T{lbrac} \Seq \NT{Entries} \Seq \T{rbrac}) \Seq \FOLLOW(\NT{Dict})) &= \{\T{lbrac}\}\\
    \FIRST(\FIRST(\NT{Entry} \Seq \T{semi} \Seq \NT{Entries}) \Seq \FOLLOW(\NT{Entries})) &= \{\T{string}\}\\
    \FIRST(\FIRST(\Null) \Seq \FOLLOW(\NT{Entries'})) &= \{\T{rbrac}\}\\
    \FIRST(\FIRST(\T{string} \Seq \T{colon} \Seq \NT{Value}) \Seq \FOLLOW(\NT{Entry})) &= \{\T{string}\}\\
    \FIRST(\FIRST(\T{int}) \Seq \FOLLOW(\NT{Value})) &= \{\T{int}\}\\
    \FIRST(\FIRST(\T{string}) \Seq \FOLLOW(\NT{Value})) &= \{\T{string}\}\\
    \FIRST(\FIRST(\T{Dict}) \Seq \FOLLOW(\NT{Value})) &= \{\T{lbrac}\}\\
  \end{aligned}
\end{equation*}

\begin{equation*}
  \begin{aligned}
    \NT{Start} &\Arrow \Lookahead{\T{lbrac}} \NT{Dict}\\
    \NT{Dict} &\Arrow \Lookahead{\T{lbrac}} \T{lbrac} \Spc \NT{Entries} \Spc \T{rbrac}\\
    \NT{Entries} &\Arrow \Lookahead{\T{string}} \NT{Entry} \Spc \T{semi} \Spc \NT{Entries} \Union \Lookahead{\T{rbrac}} \Null\\
    \NT{Entry} &\Arrow \Lookahead{\T{string}} \T{string} \Spc \T{colon} \Spc \NT{Item}\\
    \NT{Item} &\Arrow \Lookahead{\T{int}} \T{int} \Union \Lookahead{\T{string}} \T{string} \Union \Lookahead{\T{lbrac}} \NT{Dict}
  \end{aligned}
\end{equation*}

\subsection{Deklaracija spremenljivke}

\subsubsection*{Jezik}
\begin{verbatim}
Int var;
static Char global;
private static String str;
public static final Int pi;
\end{verbatim}

\subsubsection*{Regularni izrazi}
\begin{equation*}
  \begin{aligned}
    \T{semi} &= \Char{;}\\
    \T{id} &= \Kleene{\{\Char{A}, \dots, \Char{Z}, \Char{a}, \dots, \Char{z}\}}\\
    \T{int} &= \Char{Int}\\
    \T{char} &= \Char{Char}\\
    \T{string} &= \Char{String}\\
    \T{public} &= \Char{public}\\
    \T{protected} &= \Char{protected}\\
    \T{private} &= \Char{private}\\
    \T{static} &= \Char{static}\\
    \T{extern} &= \Char{extern}\\
    \T{final} &= \Char{final}\\
    \T{volatile} &= \Char{volatile}\\
  \end{aligned}
\end{equation*}

\subsubsection*{Gramatika}
\begin{equation*}
  \begin{aligned}
    \NT{Start} &\Arrow \NT{Decl}\\
    \NT{Decl} &\Arrow \NT{Scope} \Spc \NT{Modifier} \Spc \NT{Qualifier} \Spc \NT{Type} \Spc \T{id} \Spc \T{semi}\\
    \NT{Scope} &\Arrow \T{public} \Union \T{protected} \Union \T{private} \Union \Null\\
    \NT{Modifier} &\Arrow \T{static} \Union \T{extern} \Union \Null\\
    \NT{Qualifier} &\Arrow \T{final} \Union \T{volatile} \Union \Null\\
    \NT{Type} &\Arrow \T{int} \Union \T{char} \Union \T{string}\\
  \end{aligned}
\end{equation*}

\subsubsection*{{\FIRST} \& {\FOLLOW}}
\begin{equation*}
  \begin{aligned}
    \FIRST(\T{semi}) &= \{\T{semi}\}\\
    \FIRST(\T{id}) &= \{\T{id}\}\\
    \FIRST(\T{int}) &= \{\T{int}\}\\
    \FIRST(\T{char}) &= \{\T{char}\}\\
    \FIRST(\T{string}) &= \{\T{string}\}\\
    \FIRST(\T{public}) &= \{\T{public}\}\\
    \FIRST(\T{protected}) &= \{\T{protected}\}\\
    \FIRST(\T{private}) &= \{\T{private}\}\\
    \FIRST(\T{static}) &= \{\T{static}\}\\
    \FIRST(\T{extern}) &= \{\T{extern}\}\\
    \FIRST(\T{final}) &= \{\T{final}\}\\
    \FIRST(\T{volatile}) &= \{\T{volatile}\}\\
    \FIRST(\NT{Type}) &= \{\T{int}, \T{char}, \T{string}\} \\
    \FIRST(\NT{Qualifier}) &= \{\T{final}, \T{volatile}\}\\
    \FIRST(\NT{Modifier}) &= \{\T{static}, \T{extern}\}\\
    \FIRST(\NT{Scope}) &= \{\T{public}, \T{protected}, \T{private}\}\\
    \FIRST(\NT{Decl}) &= \begin{aligned}[t]\{&\T{public}, \T{protected}, \T{private}, \T{static}, \T{extern},\\
    &\T{final}, \T{volatile}, \T{int}, \T{char}, \T{string}\}\end{aligned}\\
    \FIRST(\NT{Start}) &= \begin{aligned}[t]\{&\T{public}, \T{protected}, \T{private}, \T{static}, \T{extern},\\
    &\T{final}, \T{volatile}, \T{int}, \T{char}, \T{string}\}\end{aligned}\\
    \FIRST(\NT{Scope} \Seq \NT{Modifier} \Seq \NT{Qualifier} \Seq \NT{Type} \Seq \T{id} \Seq \T{semi}) &= \begin{aligned}[t]\{&\T{public}, \T{protected}, \T{private}, \T{static}, \T{extern},\\
    &\T{final}, \T{volatile}, \T{int}, \T{char}, \T{string}\}\end{aligned}\\[1em]
    \FOLLOW(\NT{Start}) &= \{\EOF\}\\
    \FOLLOW(\NT{Decl}) &= \{\EOF\}\\
    \FOLLOW(\NT{Scope}) &= \{\T{static}, \T{extern}, \T{final}, \T{volatile}, \T{int}, \T{char}, \T{string}\}\\
    \FOLLOW(\NT{Modifier}) &= \{\T{final}, \T{volatile}, \T{int}, \T{char}, \T{string}\}\\
    \FOLLOW(\NT{Qualifier}) &= \{\T{int}, \T{char}, \T{string}\}\\
  \end{aligned}
\end{equation*}

\begin{equation*}
  \begin{aligned}
    \FIRST(\FIRST(\NT{Decl}) \Seq \FOLLOW(\NT{Start})) &= \begin{aligned}[t]\{&\T{public}, \T{protected}, \T{private}, \T{static}, \T{extern},\\
    &\T{final}, \T{volatile}, \T{int}, \T{char}, \T{string}\}\end{aligned}\\
    \FIRST(\FIRST(\T{public}) \Seq \FOLLOW(\NT{Scope})) &= \{\T{public}\}\\
    \FIRST(\FIRST(\T{protected}) \Seq \FOLLOW(\NT{Scope})) &= \{\T{protected}\}\\
    \FIRST(\FIRST(\T{private}) \Seq \FOLLOW(\NT{Scope})) &= \{\T{private}\}\\
    \FIRST(\FIRST(\Null) \Seq \FOLLOW(\NT{Scope})) &= \{\T{static}, \T{extern}, \T{final}, \T{volatile}, \T{int}, \T{char}, \T{string}\}\\
    \FIRST(\FIRST(\T{static}) \Seq \FOLLOW(\NT{Modifier})) &= \{\T{static}\}\\
    \FIRST(\FIRST(\T{extern}) \Seq \FOLLOW(\NT{Modifier})) &= \{\T{extern}\}\\
    \FIRST(\FIRST(\Null) \Seq \FOLLOW(\NT{Modifier})) &= \{\T{final}, \T{volatile}, \T{int}, \T{char}, \T{string}\}\\
    \FIRST(\FIRST(\T{final}) \Seq \FOLLOW(\NT{Qualifier})) &= \{\T{static}\}\\
    \FIRST(\FIRST(\T{volatile}) \Seq \FOLLOW(\NT{Qualifier})) &= \{\T{extern}\}\\
    \FIRST(\FIRST(\Null) \Seq \FOLLOW(\NT{Qualifier})) &= \{\T{int}, \T{char}, \T{string}\}\\
    \FIRST(\FIRST(\T{int}) \Seq \FOLLOW(\NT{Type})) &= \{\T{int}\}\\
    \FIRST(\FIRST(\T{char}) \Seq \FOLLOW(\NT{Type})) &= \{\T{char}\}\\
    \FIRST(\FIRST(\T{string}) \Seq \FOLLOW(\NT{Type})) &= \{\T{string}\}\\
  \end{aligned}
\end{equation*}

\begin{equation*}
  \begin{aligned}
    \NT{Start} &\Arrow \Lookahead{\T{public}, \T{protected}, \T{private}, \T{static}, \T{extern}, \T{final}, \T{volatile}, \T{int}, \T{char}, \T{string}} \NT{Decl}\\
    \NT{Decl} &\Arrow \Lookahead{\T{public}, \T{protected}, \T{private}, \T{static}, \T{extern}, \T{final}, \T{volatile}, \T{int}, \T{char}, \T{string}} \NT{Scope} \Spc \NT{Modifier} \Spc \NT{Qualifier} \Spc \NT{Type} \Spc \T{id} \Spc \T{semi}\\
    \NT{Scope} &\Arrow \Lookahead{\T{public}} \T{public} \Union \Lookahead{\T{protected}} \T{protected} \Union \Lookahead{\T{private}} \T{private} \Union \Lookahead{\T{static}, \T{extern}, \T{final}, \T{volatile}, \T{int}, \T{char}, \T{string}} \Null\\
    \NT{Modifier} &\Arrow \Lookahead{\T{static}} \T{static} \Union \Lookahead{\T{extern}} \T{extern} \Union \Lookahead{\T{final}, \T{volatile}, \T{int}, \T{char}, \T{string}} \Null\\
    \NT{Qualifier} &\Arrow \Lookahead{\T{final}} \T{final} \Union \Lookahead{\T{volatile}} \T{volatile} \Union \Lookahead{\T{int}, \T{char}, \T{string}} \Null\\
    \NT{Type} &\Arrow \Lookahead{\T{int}}  \T{int} \Union \Lookahead{\T{char}} \T{char} \Union \Lookahead{\T{string}} \T{string}\\
  \end{aligned}
\end{equation*}

\subsection{Deklaracija funkcije}

\subsubsection*{Jezik}
\begin{verbatim}
Int fun();
Int add(Int x, Int y);
Bool isZero(Int x);
Unit print();
\end{verbatim}

\subsubsection*{Regularni izrazi}
\begin{equation*}
  \begin{aligned}
    \T{semi} &= \Char{;}\\
    \T{comma} &= \Char{,}\\
    \T{lparen} &= \Char{(}\\
    \T{rparen} &= \Char{)}\\
    \T{id} &= \KleenePlus{\{\Char{A}, \dots, \Char{Z}, \Char{a}, \dots, \Char{z}\}}\\
    \T{unit} &= \Char{Unit}\\
    \T{int} &= \Char{Int}\\
    \T{char} &= \Char{Char}\\
    \T{string} &= \Char{String}\\
  \end{aligned}
\end{equation*}

\subsubsection*{Gramatika}
\begin{equation*}
  \begin{aligned}
    \NT{Start} &\Arrow \NT{Decl}\\
    \NT{Decl} &\Arrow \NT{Type} \Spc \T{id} \Spc \T{lparen} \Spc \NT{Args} \Spc \T{rparen} \Spc \T{semi}\\
    \NT{Args} &\Arrow \NT{Arg} \Spc \NT{Args'} \Union \Null\\
    \NT{Args'} &\Arrow \T{comma} \Spc \NT{Arg} \Spc \NT{Args'} \Union \Null\\
    \NT{Arg} &\Arrow \NT{Type} \Spc \T{id}\\
    \NT{Type} &\Arrow \T{unit} \Union \T{int} \Union \T{char} \Union \T{string}\\
  \end{aligned}
\end{equation*}

\subsubsection*{{\FIRST} \& {\FOLLOW}}
\begin{equation*}
  \begin{aligned}
    \NT{Start} &\Arrow \Lookahead{\T{unit}, \T{int}, \T{char}, \T{string}} \NT{Decl}\\
    \NT{Decl} &\Arrow \Lookahead{\T{unit}, \T{int}, \T{char}, \T{string}} \NT{Type} \Spc \T{id} \Spc \T{lparen} \Spc \NT{Args} \Spc \T{rparen} \Spc \T{semi}\\
    \NT{Args} &\Arrow \Lookahead{\T{unit}, \T{int}, \T{char}, \T{string}} \NT{Arg} \Spc \NT{Args'} \Union \Lookahead{\T{rparen}} \Null\\
    \NT{Args'} &\Arrow \Lookahead{\T{comma}} \T{comma} \Spc \NT{Arg} \Spc \NT{Args'} \Union \Lookahead{\T{rparen}} \Null \\
    \NT{Arg} &\Arrow \Lookahead{\T{unit}, \T{int}, \T{char}, \T{string}} \NT{Type} \Spc \T{id}\\
    \NT{Type} &\Arrow \Lookahead{\T{unit}} \T{unit} \Union \Lookahead{\T{int}} \T{int} \Union \Lookahead{\T{char}} \T{char} \Union \Lookahead{\T{string}} \T{string}\\
  \end{aligned}
\end{equation*}

\subsection{Preprosta Boolova algebra}
\begin{verbatim}
true
true & false => false
true | false & true
(true | false) & true
false => true
\end{verbatim}

\subsubsection*{Regularni izrazi}
\begin{equation*}
  \begin{aligned}
    \T{arrow} &= \Char{=>}\\
    \T{and} &= \Char{\&}\\
    \T{or} &= \Char{|}\\
    \T{true} &= \Char{true}\\
    \T{false} &= \Char{false}\\
    \T{lparen} &= \Char{(}\\
    \T{rparen} &= \Char{)}\\
  \end{aligned}
\end{equation*}

\subsubsection*{Gramatika}
\begin{align*}
  \NT{Start} &\Arrow \NT{Impl}\\[1em]
  \NT{Impl} &\Arrow \NT{Disj} \Spc \NT{Impl'}\\
  \NT{Impl'} &\Arrow \T{arrow} \Spc \NT{Disj} \Spc \NT{Impl'} \Union \Null\\[1em]
  \NT{Disj} &\Arrow \NT{Conj} \Spc \NT{Disj'}\\
  \NT{Disj'} &\Arrow \T{or} \Spc \NT{Conj} \Spc \NT{Disj'} \Union \Null\\[1em]
  \NT{Conj} &\Arrow \NT{Primary} \Spc \NT{Conj'}\\
  \NT{Conj'} &\Arrow \T{and} \Spc \NT{Primary} \Spc \NT{Conj'} \Union \Null\\[1em]
  \NT{Primary} &\Arrow \T{true} \Union \T{false} \Union \T{lparen} \Spc \NT{Impl} \Spc \T{rparen}
\end{align*}

\subsubsection*{{\FIRST} \& {\FOLLOW}}
\begin{align*}
  \NT{Start} &\Arrow \Lookahead{\T{true}, \T{false}, \T{lparen}} \NT{Impl}\\[1em]
  \NT{Impl} &\Arrow \Lookahead{\T{true}, \T{false}, \T{lparen}} \NT{Disj} \Spc \NT{Impl'}\\
  \NT{Impl'} &\Arrow \Lookahead{\T{arrow}} \T{arrow} \Spc \NT{Disj} \Spc \NT{Impl'} \Union \Lookahead{\T{rparen}, \T{\EOF}} \Null\\[1em]
  \NT{Disj} &\Arrow \Lookahead{\T{true}, \T{false}, \T{lparen}} \NT{Conj} \Spc \NT{Disj'}\\
  \NT{Disj'} &\Arrow \Lookahead{\T{or}} \T{or} \Spc \NT{Conj} \Spc \NT{Disj'} \Union \Lookahead{\T{arrow}, \T{rparen}, \T{\EOF}} \Null\\[1em]
  \NT{Conj} &\Arrow \Lookahead{\T{true}, \T{false}, \T{lparen}} \NT{Primary} \Spc \NT{Conj'}\\
  \NT{Conj'} &\Arrow \Lookahead{\T{and}} \T{and} \Spc \NT{Primary} \Spc \NT{Conj'} \Union \Lookahead{\T{or}, \T{arrow}, \T{rparen}, \T{\EOF}} \Null\\[1em]
  \NT{Primary} &\Arrow \Lookahead{\T{true}} \T{true} \Union \Lookahead{\T{false}} \T{false} \Union \Lookahead{\T{lparen}} \T{lparen} \Spc \NT{Impl} \Spc \T{rparen}
\end{align*}

\subsection{BC}
\begin{verbatim}
  a = 1;
  b = 2;
  print a + b;
\end{verbatim}

\subsubsection*{Regularni izrazi}
\begin{equation*}
  \begin{aligned}
    \T{int} &= \KleenePlus{\{\Char{0}, \dots, \Char{9}\}}\\
    \T{id} &= \KleenePlus{\{\Char{a}, \dots, \Char{z}\}}\\
    \T{asign} &= \Char{=}\\
    \T{semi} &= \Char{;}\\
    \T{plus} &= \Char{+}\\
    \T{minus} &= \Char{-}\\
    \T{times} &= \Char{*}\\
    \T{divide} &= \Char{/}\\
    \T{lparen} &= \Char{(}\\
    \T{rparen} &= \Char{)}\\
    \T{print} &= \Char{print}\\
  \end{aligned}
\end{equation*}

\subsubsection*{Gramatika}
\begin{equation*}
  \begin{aligned}
    \NT{Stmts} &\Arrow \NT{Stmt} \Spc \T{semi} \Spc \NT{Stmts} \Union \Null\\
    \NT{Stmt} &\Arrow \T{id} \Spc \T{assign} \Spc \NT{Expr} \Union \T{print} \Spc \NT{Expr}\\
    \NT{Expr} &\Arrow \NT{Term} \Spc \NT{Expr'}\\
    \NT{Expr'} &\Arrow \T{plus} \Spc \NT{Term} \Spc \NT{Expr'} \Union \T{minus} \Spc \NT{Term} \Spc \NT{Expr'} \Union \Null\\
    \NT{Term} &\Arrow \NT{Fac} \Spc \NT{Term'}\\
    \NT{Term'} &\Arrow \T{times} \Spc \NT{Fac} \Spc \NT{Term'} \Union \T{divide} \Spc \NT{Fac} \Spc \NT{Term'} \Union \Null\\
    \NT{Fac} &\Arrow \T{plus} \Spc \NT{Value} \Union \T{minus} \Spc \NT{Value} \Union \NT{Value}\\
    \NT{Value} &\Arrow \T{int} \Union \T{id} \Union \T{lparen} \Spc \NT{Expr} \Spc \T{rparen}
  \end{aligned}
\end{equation*}

\subsection{Lisp}
\begin{verbatim}
  (cons 1 (cons 1 nil))
\end{verbatim}
\begin{verbatim}
  (cons (+ 1 1) 2)
\end{verbatim}
\begin{verbatim}
  (list 1 2 3)
\end{verbatim}
